### 2013-07-22 docs/Jesse/Dissertation/globalLocalDPG.tex
updating diss figs

%&pdflatex
\documentclass[11pt,onecolumn]{scrartcl}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsfonts,mathrsfs,amsthm}
\usepackage[top=2cm,bottom=3cm,left=2.5cm,right=2cm]{geometry}
\usepackage{amssymb}
\usepackage{amscd}
\usepackage{listings}
\usepackage{array}
\usepackage{mathtools}
\usepackage{dsfont}
\usepackage{graphicx}
\usepackage{pdfpages}
\usepackage[textsize=footnotesize,color=green]{todonotes}
\usepackage{algorithm, algorithmic}
\usepackage{array}
\usepackage{bm}
\usepackage{tikz}
\usepackage{subfigure}
\usepackage[normalem]{ulem}

\newcommand{\bs}[1]{\boldsymbol{#1}}
\DeclareMathOperator{\diag}{diag}

\newcommand{\equaldef}{\stackrel{\mathrm{def}}{=}}

\newcommand{\tablab}[1]{\label{tab:#1}}
\newcommand{\tabref}[1]{Table~\ref{tab:#1}}

\newcommand{\theolab}[1]{\label{theo:#1}}
\newcommand{\theoref}[1]{\ref{theo:#1}}
\newcommand{\eqnlab}[1]{\label{eq:#1}}
\newcommand{\eqnref}[1]{\eqref{eq:#1}}
\newcommand{\seclab}[1]{\label{sec:#1}}
\newcommand{\secref}[1]{\ref{sec:#1}}
\newcommand{\lemlab}[1]{\label{lem:#1}}
\newcommand{\lemref}[1]{\ref{lem:#1}}

\newcommand{\mb}[1]{\mathbf{#1}}
\newcommand{\mbb}[1]{\mathbb{#1}}
\newcommand{\mc}[1]{\mathcal{#1}}
\newcommand{\nor}[1]{\left\| #1 \right\|}
\newcommand{\snor}[1]{\left| #1 \right|}
\newcommand{\LRp}[1]{\left( #1 \right)}
\newcommand{\LRs}[1]{\left[ #1 \right]}
\newcommand{\LRa}[1]{\left\langle #1 \right\rangle}
\newcommand{\LRc}[1]{\left\{ #1 \right\}}
\newcommand{\LRb}[1]{\left| #1 \right|}

\newcommand{\tanbui}[2]{\textcolor{blue}{\sout{#1}} \textcolor{red}{#2}}
\newcommand{\Grad} {\ensuremath{\nabla}}
\newcommand{\Div} {\ensuremath{\nabla\cdot}}
\newcommand{\Nel} {\ensuremath{{N^\text{el}}}}
\newcommand{\jump}[1] {\ensuremath{\LRs{\!\left[#1\right]\!}}}
\newcommand{\uh}{\widehat{u}}
\newcommand{\fnh}{\widehat{f}_n}
\renewcommand{\L}{L^2\LRp{\Omega}}
\newcommand{\pO}{\partial\Omega}
\newcommand{\Gh}{\Gamma_h}
\newcommand{\Gm}{\Gamma_{-}}
\newcommand{\Gp}{\Gamma_{+}}
\newcommand{\Go}{\Gamma_0}
\newcommand{\Oh}{\Omega_h}

\newcommand{\eval}[2][\right]{\relax
  \ifx#1\right\relax \left.\fi#2#1\rvert}

\def\etal{{\it et al.~}}

\newcommand{\vect}[1]{\ensuremath\boldsymbol{#1}}
\newcommand{\tensor}[1]{\underline{\vect{#1}}}
\newcommand{\del}{\Delta}
\newcommand{\grad}{\nabla}
\newcommand{\curl}{\grad \times}
\renewcommand{\div}{\grad \cdot}
\newcommand{\ip}[1]{\left\langle #1 \right\rangle}
\newcommand{\eip}[1]{a\left( #1 \right)}
\newcommand{\pd}[2]{\frac{\partial#1}{\partial#2}}
\newcommand{\pdd}[2]{\frac{\partial^2#1}{\partial#2^2}}

\newcommand{\circone}{\ding{192}}
\newcommand{\circtwo}{\ding{193}}
\newcommand{\circthree}{\ding{194}}
\newcommand{\circfour}{\ding{195}}
\newcommand{\circfive}{\ding{196}}

\def\arr#1#2#3#4{\left[
\begin{array}{cc}
#1 & #2\\
#3 & #4\\
\end{array}
\right]}
\def\vecttwo#1#2{\left[
\begin{array}{c}
#1\\
#2\\
\end{array}
\right]}
\def\vectthree#1#2#3{\left[
\begin{array}{c}
#1\\
#2\\
#3\\
\end{array}
\right]}
\def\vectfour#1#2#3#4{\left[
\begin{array}{c}
#1\\
#2\\
#3\\
#4\\
\end{array}
\right]}

\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}

\newcommand{\G} {\Gamma}
\newcommand{\Gin} {\Gamma_{in}}
\newcommand{\Gout} {\Gamma_{out}}

\newtheorem{remark}{Remark}

\author{Jesse Chan\textsuperscript{a}, Jay Gopalakrishnan\textsuperscript{b}, and Leszek Demkowicz\textsuperscript{a}}

%\title{$\epsilon$-explicit analysis of DPG for convection-dominated diffusion}
\title{Global properties of DPG test spaces for convection-diffusion problems}
\date{}
\begin{document}

\maketitle
\begin{center}
\textsuperscript{a} Institute for Computational Engineering and Sciences, \\University of Texas at Austin, \\Austin, TX 78712, USA\\
\end{center}

\begin{center}
\textsuperscript{b} Department of Mathematics\\Portland State University, \\
Portland, OR 97207, USA
%\textsuperscript{b} Facultad de Matem\'aticas, \\Pontificia Universidad Cat\'olica de Chile,\\
%Avenida Vicu\~na Mackenna 4860, Santiago, Chile
\end{center}

%\tableofcontents

\section{Introduction to DPG}

The Discontinuous Petrov-Galerkin method was originally introduced by Demkowicz and Gopalakrishnan in 2009 as a way to attain automatic inf-sup stability for any well-posed variational problem through the construction of optimal test functions \cite{DPG2}.  The method was later shown to be equivalent to the minimum residual method applied to the operator residual corresponding to a variational formulation \cite{DPG2, ChanHeuerBui-ThanhDemkowicz12}.  A more detailed overview of the current state of DPG is available at \cite{overviewDPG}; we give only a brief introduction here.

The derivation of the DPG method can be briefly summarized as follows: assume we are given a trial space $U$, a discrete trial space $U_h \subset U$, a Hilbert test space $V$, and a well-posed (in the inf-sup sense) variational problem: find $u\in U$  such that
\begin{align}
\label{variational}
&b(u,v) = l(v), \quad \forall v\in V, 
\end{align}
where $b(u,v)$ is a bilinear form and $l \in V'$. If we identify the variational operator $B: U\rightarrow V'$ such that $\LRa{Bu,v} \coloneqq b(u,v)$, we can write the above variational formulation as an operator equation in $V'$
\[
Bu = l,
\]
where inf-sup well-posedness of the variational formulation translates to boundedness from above and below of the operator $B$.

Let $u_h \in U_h$ now be a discrete approximation to $u$. Seeking the minimization of the discrete residual $\frac{1}{2} \nor{Bu_h-l}^2_{V'}$, we arrive at the normal equations 
\begin{equation}
\label{dualNormal}
\LRp{Bu_h-l,B\delta u}_{V'} = 0, \quad \forall \delta u \in U_h.  
\end{equation}
Since $V$ is Hilbert, we can introduce the Riesz map $R_V:V \rightarrow V'$, an isometric isomorphism such that $\LRa{R_V v,\cdot} = \LRp{v,\cdot}_V$. By taking the inverse of the Riesz map, we can transform the normal equations in $V'$ to a set of normal equations in $V$
\[
\LRp{R_V^{-1}\LRp{Bu_h-l},R_V^{-1}\LRp{B\delta u}}_{V} = 0, \quad \forall \delta u \in U_h.  
\]
Using the definitions of the Riesz map $R_V$ and variational operator $B$, we have that
\begin{align*}
\LRp{R_V^{-1}\LRp{Bu_h-l},R_V^{-1}\LRp{B\delta u}}_{V} = 0, \quad \forall \delta u \in U_h \\
\rightarrow \LRa{Bu_h-l,R_V^{-1}\LRp{B\delta u}}_{V} = 0, \quad \forall \delta u \in U_h \\
\rightarrow b\LRp{u_h,R_V^{-1} B\delta u} - l\LRp{R_V^{-1} B\delta u} = 0, \quad \forall \delta u \in U_h.
\end{align*}
In other words, the minimization of the operator residual associated with a given variational form corresponds directly to a Petrov-Galerkin formulation, where test functions are determined under the so-called \textit{trial-to-test} operator $R_V^{-1}B$, which, given functions in the discrete trial space $U_h$,  returns back corresponding test functions which span the discrete test space.

Solutions $u$ to the above problem enjoy the following properties: 
\begin{enumerate}
\item If we define the energy norm 
\[
\nor{u}_E = \nor{Bu}_{V'} = \sup_{v\in V\setminus\{0\}}\frac{\LRb{b(u,v)}}{\nor{v}_V},
\]
then DPG is optimal in the energy norm $\nor{u}_E$, which is induced through the energy inner product
\[
\LRp{v,w}_E = \LRp{Bv,Bw}_{V'} = \LRp{R_V^{-1}Bv, R_V^{-1}Bw}_V.
\]
\item The exact energy error $\nor{u-u_h}_E$ is computable without knowing $u$ explicitly, owing to the fact that
\[
\nor{u-u_h}_E = \nor{B(u-u_h)}_{V'} = \nor{{l-Bu_h}}_{V'} = \sup_{v\in V\setminus\{0\}}\frac{l(v)-b(u,v)}{\nor{v}_V},
\]
which can be computed by first computing an \textit{error representation function} $e$ and then evaluating $\nor{e}_V$.  The error representation function is determined by solving the problem
\[
\LRp{e,\delta v}_V = l(\delta v)-b(u,\delta v), \quad \delta v\in V.
\]
This property is simply a result of the minimum residual nature of DPG; the energy error is simply the residual, measured in the proper norm.  
\item Let $\{u_i\}_{i = 0}^{i = N}$ be discrete trial functions and $v_{u_i}$ be the corresponding optimal test functions (solutions of Problem (\ref{aux}) below).  The discrete system resulting from DPG is symmetric positive-definite; this can be seen from the identity
\[
b(u_i,v_{u_j}) = \LRp{v_{u_i},v_{u_j}}_V = \LRp{v_{u_j},v_{u_i}}_V = b(u_j,v_{u_i}).
\]
Positive-definiteness is again a natural consequence of the minimum-residual nature of DPG.  
\end{enumerate}

\subsection{Broken test spaces}

To determine test functions under DPG, we must invert the Riesz map by determining $R_V^{-1} B\delta u$, which is done by solving the auxiliary variational problem
\begin{equation}
\label{aux}
(v,\delta v)_V = b\LRp{\delta u,\delta v}, \quad \forall \delta v\in V.  
\end{equation}
Unfortunately, this amounts to both an infinite-dimensional and global problem if $V$ is not chosen carefully.  For example, if $V = H^1(\Omega)$ and $\LRp{\cdot, \cdot }_V$ corresponded to the $H^1$ Sobolev inner product  $\LRp{v,\delta v}_{L^2(\Omega)} + \LRp{\grad v,\grad \delta v}_{L^2(\Omega)}$, solving for a single optimal test function would be equivalent to solving the Poisson equation exactly over the entire domain.  However, we can both localize and make solving Problem~(\ref{aux}) computationally feasible by choosing for $V$ a \textit{broken} test space and by approximating the solution to (\ref{aux}) using a discrete space $V_h\subset V$.

We begin by assuming we are given some triangulation $\Omega_h$ of $\Omega$ such that $\bar{\Omega} = \bigcup_{K\in \Omega_h}\bar{K}$.  We can adopt for $V$ the broken test space
\[
V(\Oh) = \bigoplus_{K\in \Omega_h}V(K).
\]
If we further assume that the inner product and norm on $V$ are localizable\footnote{A localizable norm $\nor{v}_{V(\Oh)}$ can be written in the form 
$$\nor{v}_{V(\Oh)}^2 = \sum_{K\in\Oh} \nor{v}_{V(K)}^2,$$ where $\nor{v}_{V(K)}$ is a norm over the element $K$.}, the solution to \eqref{aux} (corresponding to the inversion of the Riesz map) can now be determined locally over each element.  In practice, these solutions are approximated by solving (\ref{aux}) over a locally conforming space $V_h$ over each element $K$, where $\dim(V_h) > \dim(U_h)$ elementwise.  Typically, if $U_h$ is of order $p$, $V_h$ is chosen to be the corresponding $H^1$ or $H({\rm div})$ conforming space of order $p + \del p$, where $\del p \geq n$, the spatial dimension \cite{practicalDPG}.  For this reason, we refer to $V_h$ as the \textit{enriched} space.  We refer to this approximated test space under $V_h$ as the approximate optimal test space $V_{{\rm opt},h}$.  
\begin{remark}
All properties of DPG carry over if $V=V_h$, the discrete inner product space, and if Problem~(\ref{aux}) is well-approximated under $V_h$, then the solution to our variational problem (\ref{variational}) over the approximate optimal test space will deliver very similar results to the solution of (\ref{variational}) over the exact optimal test space.  
\end{remark}

\subsection{The ultra-weak variational formulation}

Up to now, the variational formulation has been left unspecified.  For several reasons, we've chosen to use the \textit{ultra-weak formulation}, which results from writing the PDE as a first-order system, integrating all derivatives by parts, and identifying boundary traces as independent unknowns, similarly to hybridized DG methods.  The formulation is given as follows: let $$\Gh = \bigcup_{K\in \Oh} \partial K$$ be the \textit{mesh skeleton}, comprising of the union of all element boundaries.  Let $Au=f$ represents the strong form of a first-order system of PDEs; the ultra-weak formulation is then
\begin{equation}
\label{variationalProblem}
b\LRp{\LRp{u,\uh},v} = \LRp{u,A_h^*v}_{\Oh} + \sum_{K \in \Oh} \LRa{\uh,v}_{\partial K} = \LRp{f,v}_{\Omega},
\end{equation}
where $u \in \L$, and $A_h^*$ is the formal adjoint of $A$ acting elementwise on a broken test space, and $\LRa{\uh,v}_{\partial K}$ is the duality pairing between the trace unknown $\uh$ and the trace of the test function $v$ on an element boundary.  Under proper regularity assumptions, we have that 
$$\sum_{K \in \Oh} \LRa{\uh,v}_{\partial K} = \LRa{\uh,\jump{v}}_{\Gh}.$$    %so $\uh \in \gamma(D\LRp{A})$, the trace space of the domain of the strong operator $A$.  
Finally, $\uh$ represents the trace of the conforming solution to $Au=f$ on the mesh skeleton $\Gh$; if we define the graph space $H_A \coloneqq \LRc{u \in U: Au\in \L},$ then $\uh$ comes from $ \widehat{H}_A(\Gh)$, the trace space of $H_A$ on $\Gh$
\[
\widehat{H}_A(\Gh) \coloneqq \LRc{ \left.u\right|_{\Gh}: u\in H_A}.
\]

Combining this variational formulation with the concept of DPG optimal test functions yields a conforming method for $u$, the field variable, and $\uh$, the trace variable. Optimal test functions are all determined locally, and optimal test functions corresponding to traces defined on the element boundary $\partial K$ have support over each element adjacent to $\partial K$.  The degrees of freedom are thus coupled together globally through the optimal test functions for trace variables.

\begin{remark}
\label{remarkDahmen}
It is possible to apply the same minimum-residual method behind DPG in an alternative fashion by casting the normal equations as a saddle-point problem, which is the approach taken by Dahmen et al.\ in \cite{DahmenVariationalStabilization}. This method requires the solution of a larger global linear system than the DPG method, but can be directly applied to arbitrary variational formulations and conforming discretizations of $V$.  
\end{remark}

\subsection{The graph test norm}

We have not yet specified the inner product $\LRp{v,\delta v}_V$, which induces the norm defining the space $V$.  Here, we derive two important ``canonical" test norms for the ultra-weak variational formulation.  We begin first with the canonical norm in $U$. Since $\uh \in \widehat{H}_A(\Gh)$, the standard norm for $\uh$ is the so-called minimum energy extension norm defined as
\begin{equation*}
\|\widehat{u}\| = \inf_{w\in \widehat{H}_A(\Gamma_h),
  \left.w\right|_{\Gh}=\widehat{u}} \|w\|_{\widehat{H}_A}.
\end{equation*}
The canonical norm for the group variable $\LRp{u,\uh}$ is then given by
\[
\|\left(u,\widehat{u}\right)\|_U^2 = \|u\|^2_{\L} + \|\widehat{u}\|^2.
\]
If we define the norm $\nor{v}_{V,U}$  through
\[
\nor{v}_{V,U}^2 = \|A_h^*v\|_{\L}^2
+\left(\sup_{\widehat{u} \in \widehat{H}_A(\Gamma_h)} \frac{\LRa{ \widehat{u},
  \jump{v} }_{\Gh}}{\|\widehat{u}\|}\right)^2, 
\]
it has been shown in \cite{Bui-ThanhDemkowiczGhattas11a, ChanHeuerBui-ThanhDemkowicz12} that the canonical norm $\nor{\LRp{u,\uh}}_U$ in $U$ induces (generates) the norm $\nor{v}_{V,U}$ in $V$; in other words, the energy norm in which DPG is optimal is equal to the canonical norm $\nor{\LRp{u,\uh}}_U$ if we choose for a test norm on $\nor{v}_{V,U}$.

The canonical norm $\nor{\LRp{u,\uh}}_U$ in $U$ provides an optimal balance between the standard norms on the field $u$ and the flux $\uh$ \cite{DPG4}. As a result, if the induced norm $\nor{v}_{V,U}$ (namely, the optimal test norm) is used to compute optimal test functions in (\ref{aux}), the finite element error in the canonical norm is the best in the norm $\nor{u}_{U}$. Unfortunately, the optimal test norm is non-localizable due to the presence of the jump term $\jump{v}$. Since the jump terms couple elements together, the evaluation of the jump terms requires contributions from all the elements in the mesh. 
Consequently, solving for an optimal test function amounts to inverting the Riesz map over the entire mesh $\Oh$, making the optimal test norm impractical.

On the other hand, since $A^*_h v \in \L$, we can use as a test norm for $v$ the broken graph test norm: 
\[
\nor{v}_V^2 =  \|A_h^*v\|_{\L}^2 + \nor{v}_{\L}^2,
\]
where we have regularized the seminorm $\nor{A_h^*v}_{\L}^2$ by adding to it the $L^2$ norm of $v$.

The norm $\nor{v}_V$ can be considered as a localization of $\nor{v}_{V,U}$ to allow for the solution of optimal test functions on an element-by-element basis, and can be considered to be the canonical norm on $V$.  In the DPG literature \cite{DPG4}, $\nor{v}_{V,U}$ is known as the {\em optimal test norm}, while $\nor{v}_{V}$ is known as the quasi-optimal or {\em graph} test norm.  The DPG method was first shown to be well-posed under the graph test norm for the Poisson and convection-diffusion equations in \cite{analysisDPG}.  This analysis was later extended to the large class of Friedrichs' systems in \cite{Bui-ThanhDemkowiczGhattas11b} and to Stokes in \cite{stokesDPG}.

It has also been shown in \cite{stokesDPG} that $\nor{v}_{V,U}$ and $\nor{v}_V$ are equivalent norms; if the operator $A$ is bounded below such that $\nor{Au}_{\L} \geq \gamma\nor{v}_{\L}$, then the equivalence constants between $\nor{v}_{V,U}$ and $\nor{v}_V$ are $O(\gamma)$.  This is important in context of \textit{singular perturbation problems}, which typically depend on some parameter $k\rightarrow 0$ or $k\rightarrow \infty$; if the constant $\gamma$ associated with the problem is independent of $k$, then the DPG method under the graph test norm is \textit{robust}, or equivalent to the $\L$-projection with constants independent of $k$.  Robustness is discussed more in Section~\ref{sec:robust} in context of the convection-diffusion equation.

\section{The ultra-weak formulation and globally conforming test spaces}

Though DPG test functions are determined locally on an element-by-element basis, it is the global properties of the test space that determine the performance of the method.  We motivate this statement first by deriving global conditions for the test space under which the ultra-weak variational formulation recovers an $L^2$ optimal solution, using the specific example of the convection-diffusion equation.

\subsection{The convection-diffusion equation}

The convection-diffusion problem models the concentration $u$ of some solvent in a convection field $\beta$ subject to diffusion of some magnitude $\epsilon > 0$ in some domain $\Omega$ with boundary $\Gamma$.  We decompose the boundary as follows:
\begin{align*}
\Gamma_{\rm in} &\coloneqq \{x\in \Gamma; \beta_n(x) < 0\}, \quad {\rm
(inflow)}\\ 
\Gamma_{\rm out} &\coloneqq \{x\in \Gamma; \beta_n(x) > 0\},
\quad {\rm (outflow)}\\
\Gamma_{0} &\coloneqq \{x\in \Gamma;\beta_n(x) = 0\},
\end{align*}
where $\beta_n \coloneqq \beta \cdot n$.

The problem is typically written in as
\begin{align*}
\div\LRp{\beta u - \epsilon \grad u} &= f, \quad \text{in } \Omega \\
u &= u_{0}, \quad \text{on } \Gamma.
\end{align*}
The problem is especially of interest as a prototypical problem for boundary layer problems in computational fluid dynamics, as solutions to the convection-diffusion problem can, for certain boundary conditions, develop strong boundary layers of width $\epsilon$ at the outflow boundary $\Gamma_{\rm out}$.

We can further write it as a system of first-order equations
\begin{align*}
\div\LRp{\beta u - \sigma} &= f\\
\frac{1}{\epsilon}\sigma - \grad u &= 0.
\end{align*}
This first order system is the starting point for the ultra-weak variational formulation, which, under the convection-diffusion equation and prior to the application of boundary data, is given as 
\begin{align*}
b\LRp{\LRp{u,\sigma, \uh, \fnh}, \LRp{v,\tau}} &=\LRa{\uh,\tau_n}_{\Gh} + \LRa{\fnh,v}_{\Gh} + \\ & \LRp{u, \Grad_h\cdot \tau - \beta\cdot \Grad_h v}_{\L} + \LRp{\sigma, \frac{1}{\epsilon}\tau + \Grad_h v}_{\L}.
\end{align*}
where $\fnh \coloneqq \beta_n u - \sigma_n$.  Trial and test spaces are specified to be 
\begin{align*}
\LRp{u,\sigma} \in \L, \fnh \in H^{-1/2}(\Gh), \uh \in H^{1/2}(\Gh)&,\\ 
v \in H^1(\Oh), \tau \in H\LRp{\rm div, \Oh}&,
\end{align*}
where $H^1(\Oh)$ and $H\LRp{\rm div, \Oh}$ represent the broken $H^1$ and $H(\rm div)$ spaces over $\Oh$.  This is discussed in more detail for the convection-diffusion equation in \cite{DPGrobustness, ChanHeuerBui-ThanhDemkowicz12}.

For the case of boundary data $\uh = u_0$ on the entire boundary $\Gamma$, our variational formulation becomes
\begin{align*}
\LRa{\uh,\tau_n}_{\Gh^0} + \LRa{\fnh,v}_{\Gh} + \LRp{u, \Grad_h\cdot \tau - \beta\cdot \Grad_h v} + \LRp{\sigma, \frac{1}{\epsilon}\tau + \Grad_h v} = \LRp{f,v} + \LRa{u_0,\tau_n}_{\Gamma}, 
\end{align*}
where $\Gh^0 = \Gh\setminus \Gamma$ is the union of all internal element edges, and is referred to as the internal skeleton, and $\Grad_h$ and $\Grad_h\cdot$ are understood to be the broken gradient and divergence, taken over each individual element.  We have also dropped the subscript for $\LRp{\cdot,\cdot}_{L^2(\Omega)}$ and, for the rest of the paper, simply refer to the $L^2$ inner product using the notation $\LRp{\cdot,\cdot}$.

For DPG, we must also specify a test norm which defines the test space.  Our focus will be on the graph test norm for convection-diffusion, which, under the ultra-weak variational formulation, 
\[
\nor{v}_{V_{\rm graph}}^2 = \nor{\grad_h\cdot\tau - \beta \cdot \grad_h v}_{L^2(\Omega)}^2 + \nor{{\epsilon}^{-1} \tau -  \grad_h v}_{L^2(\Omega)}^2 + \nor{v}_{L^2(\Omega)}^2
\]
where $\grad_h$ and $\div_h$ are understood to act elementwise.\footnote{Since $\nor{A^*_hv}$ is not positive definite on its own, we typically add an $L^2$ term for all components of the test function; however, here the $L^2$ norm of $\tau$ is neglected as it is not required to preserve positive-definiteness of the norm.}

Though our focus is on the convection-diffusion equation, we will attempt to relate concepts to a more general framework and notation when possible.  Overloading the notation $\uh \coloneqq \LRp{\uh,\fnh}$, $u \coloneqq \LRp{u,\sigma}$, and $v \coloneqq \LRp{v,\tau}$, we can define the operator $A_h^*: V(\Oh)\rightarrow \L$ through its action restricted to an individual element $K$
\[
\left.A_h^*v\right|_K = \LRp{\div\tau - \beta \cdot \grad v, {\epsilon}^{-1} \tau -  \grad v}, \quad \text{on } K \in \Oh.
\]
We then have the abstract representation of both the ultra-weak variational formulation and the graph test norm as
\begin{align*}
b\LRp{\LRp{u,\uh},v} &\coloneqq \LRa{\uh,v} + \LRp{u,A^*_h v}_{\L} \\
\nor{v}_V^2 &\coloneqq \nor{A_h^*v}_{\L}^2 + \nor{v}_{\L}^2
\end{align*}
From this point onward, we will continue to overload our abstract notation in order to connect more general concepts with the concrete example of the convection-diffusion equation.

@@

Let $V_{\rm opt} = \{v_{\delta u} \in V: v_{\delta u}= R_V^{-1}B\delta u, \delta u \in U_h\}$ be the space of locally determined DPG test functions, and let 
\[
\tilde{V}_{\rm opt} = \{\tilde{v}_{\delta u} \in \tilde{V}: \tilde{v}_{\delta u} = R_{V}^{-1}B\delta u, \delta u \in U_h\}
\]
be the space of optimal test functions determined \textit{globally} over the weakly conforming space $\tilde{V}$.  In other words, the optimal test functions that span $\tilde{V}_{\rm opt}$ are the result of the inversion of the Riesz operator \textit{globally}, over the entire mesh (the idea is not new - the concept of globally optimal test functions was first introduced in \cite{DPG3pub} to prove mesh-independence). The following lemma concerning the test space spanned by the locally computed optimal test functions of DPG was proven first by Demkowicz and Gopalakrishnan in \cite{overviewDPG}, which we reproduce briefly here: 
\begin{lemma}
\label{lemma1}
$\tilde{V}_{\rm opt} \subseteq V_{\rm opt}$.
\end{lemma}
\begin{proof}
We note first that, because $V_{\rm opt} \subseteq V$, we can orthogonally decompose $V = V_{\rm opt} \bigoplus V_{\rm opt}^\perp$, where, for any $v_{\rm opt}\in V_{\rm opt}$, $\LRp{v_{\rm opt},v^\perp}_V = 0$ for all $v^\perp \in V_{\rm opt}^\perp$.  Let us now choose a globally conforming test function $\tilde{v}\in \tilde{V}_{\rm opt}$.  Since $\tilde{V}_{\rm opt} \subseteq V$, we can decompose $\tilde{v} = v_{\rm opt} + v_{\rm opt}^\perp$.  Demonstrating that $v_{\rm opt}^\perp = 0$ proves the lemma.

>>>>

%\subsection{The convection-diffusion equation}
%
%The convection-diffusion problem models the concentration $u$ of some solvent in a convection field $\beta$ subject to diffusion of some magnitude $\epsilon > 0$ in some domain $\Omega$ with boundary $\Gamma$.  We decompose the boundary as follows:
%\begin{align*}
%\Gamma_{\rm in} &\coloneqq \{x\in \Gamma; \beta_n(x) < 0\}, \quad {\rm
%(inflow)}\\ 
%\Gamma_{\rm out} &\coloneqq \{x\in \Gamma; \beta_n(x) > 0\},
%\quad {\rm (outflow)}\\
%\Gamma_{0} &\coloneqq \{x\in \Gamma;\beta_n(x) = 0\},
%\end{align*}
%where $\beta_n \coloneqq \beta \cdot n$.
%
%The problem is typically written in as
%\begin{align*}
%\div\LRp{\beta u - \epsilon \grad u} &= f, \quad \text{in } \Omega \\
%u &= u_{0}, \quad \text{on } \Gamma.
%\end{align*}
%The problem is especially of interest as a prototypical problem for boundary layer problems in computational fluid dynamics, as solutions to the convection-diffusion problem can, for certain boundary conditions, develop strong boundary layers of width $\epsilon$ at the outflow boundary $\Gamma_{\rm out}$.    
%
%We can further write it as a system of first-order equations
%\begin{align*}
%\div\LRp{\beta u - \sigma} &= f\\
%\frac{1}{\epsilon}\sigma - \grad u &= 0.
%\end{align*}
%This first order system is the starting point for the ultra-weak variational formulation, which, under the convection-diffusion equation and prior to the application of boundary data, is given as 
%\begin{align*}
%b\LRp{\LRp{u,\sigma, \uh, \fnh}, \LRp{v,\tau}} &=\LRa{\uh,\tau_n}_{\Gh} + \LRa{\fnh,v}_{\Gh} + \\ & \LRp{u, \Grad_h\cdot \tau - \beta\cdot \Grad_h v}_{\L} + \LRp{\sigma, \frac{1}{\epsilon}\tau + \Grad_h v}_{\L}.
%\end{align*}
%where $\fnh \coloneqq \beta_n u - \sigma_n$.  Trial and test spaces are specified to be 
%\begin{align*}
%\LRp{u,\sigma} \in \L, \fnh \in H^{-1/2}(\Gh), \uh \in H^{1/2}(\Gh)&,\\ 
%v \in H^1(\Oh), \tau \in H\LRp{\rm div, \Oh}&,
%\end{align*}
%where $H^1(\Oh)$ and $H\LRp{\rm div, \Oh}$ represent the broken $H^1$ and $H(\rm div)$ spaces over $\Oh$.  This is discussed in more detail for the convection-diffusion equation in \cite{DPGrobustness, ChanHeuerBui-ThanhDemkowicz12}.
%
%For the case of boundary data $\uh = u_0$ on the entire boundary $\Gamma$, our variational formulation becomes
%\begin{align*}
%\LRa{\uh,\tau_n}_{\Gh^0} + \LRa{\fnh,v}_{\Gh} + \LRp{u, \Grad_h\cdot \tau - \beta\cdot \Grad_h v} + \LRp{\sigma, \frac{1}{\epsilon}\tau + \Grad_h v} = \LRp{f,v} + \LRa{u_0,\tau_n}_{\Gamma}, 
%\end{align*}
%where $\Gh^0 = \Gh\setminus \Gamma$ is the union of all internal element edges, and is referred to as the internal skeleton, and $\Grad_h$ and $\Grad_h\cdot$ are understood to be the broken gradient and divergence, taken over each individual element.  We have also dropped the subscript for $\LRp{\cdot,\cdot}_{L^2(\Omega)}$ and, for the rest of the paper, simply refer to the $L^2$ inner product using the notation $\LRp{\cdot,\cdot}$.

For DPG, we must also specify a test norm which defines the test space.  Our focus will be on the graph test norm for convection-diffusion, which, under the ultra-weak variational formulation, 
\[
\nor{\LRp{v,\tau}}_{V_{\rm graph}}^2 = \nor{\grad_h\cdot\tau - \beta \cdot \grad_h v}_{L^2(\Omega)}^2 + \nor{{\epsilon}^{-1} \tau -  \grad_h v}_{L^2(\Omega)}^2 + \nor{v}_{L^2(\Omega)}^2, 
\]
where $\grad_h$ and $\grad_h\cdot$ are understood to act elementwise.\footnote{Since $\nor{A^*_hv}$ is not positive definite on its own, we typically add an $L^2$ term for all components of the test function; however, here the $L^2$ norm of $\tau$ is neglected as it is not required to preserve positive-definiteness of the norm.}

Though our focus is on the convection-diffusion equation, we will attempt to relate concepts to a more general framework and notation when possible.  Overloading the notation $\uh \coloneqq \LRp{\uh,\fnh}$, $u \coloneqq \LRp{u,\sigma}$, and $v \coloneqq \LRp{v,\tau}$, we can define the operator $A_h^*: V(\Oh)\rightarrow \L$ through its action restricted to an individual element $K$
\[
\left.A_h^*v\right|_K = \LRp{\div\tau - \beta \cdot \grad v, {\epsilon}^{-1} \tau -  \grad v} \quad \text{on } K \in \Oh.
\]
We then have the abstract representation of both the ultra-weak variational formulation and the graph test norm as
\begin{align*}
b\LRp{\LRp{u,\uh},v} &\coloneqq \LRa{\uh,\jump{v}} + \LRp{u,A^*_h v}_{\L} \\
\nor{v}_V^2 &\coloneqq \nor{A_h^*v}_{\L}^2 + \nor{v}_{\L}^2
\end{align*}
From this point onward, we will continue to overload our abstract notation in order to connect more general concepts with the concrete example of the convection-diffusion equation.

@@

Let $V_{\rm opt} = \{v_{\delta u} \in V: v_{\delta u}= R_V^{-1}B\delta u, \delta u \in U_h\}$ be the space of locally determined DPG test functions, and let 
\[
\tilde{V}_{\rm opt} = \{\tilde{v}_{\delta u} \in \tilde{V}: \tilde{v}_{\delta u} = R_{V}^{-1}B\delta u, \delta u \in U_h\}
\]
be the space of optimal test functions determined \textit{globally} over the weakly conforming space $\tilde{V}$.  In other words, the optimal test functions that span $\tilde{V}_{\rm opt}$ are the result of the inversion of the Riesz operator \textit{globally}, over the entire mesh (the idea is not new -- the concept of globally optimal test functions was first introduced in \cite{DPG3} to prove mesh-independence). The following lemma concerning the test space spanned by the locally computed optimal test functions of DPG was proven first by Demkowicz and Gopalakrishnan in \cite{overviewDPG}, which we reproduce briefly here.
\begin{lemma}
\label{lemma1}
$\tilde{V}_{\rm opt} \subseteq V_{\rm opt}$.
\end{lemma}
\begin{proof}
We note first that, because $V_{\rm opt} \subseteq V$, we can orthogonally decompose $V = V_{\rm opt} \bigoplus V_{\rm opt}^\perp$, where, for any $v_{\rm opt}\in V_{\rm opt}$, $\LRp{v_{\rm opt},v^\perp}_V = 0$ for all $v^\perp \in V_{\rm opt}^\perp$.  Let us now choose a globally conforming test function $\tilde{v}\in \tilde{V}_{\rm opt}$.  Since $\tilde{V}_{\rm opt} \subseteq V$, we can decompose $\tilde{v} = v_{\rm opt} + v_{\rm opt}^\perp$.  Demonstrating that $v_{\rm opt}^\perp = 0$ proves the lemma.
